On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-09-06 paper.tex
Minor

\section{A variant of Rehmann theorem}
Let $A$ be arbitrary commutative unital ring and $\mathfrak{m}$ be its ideal.
Denote by $B$ the subring $\mathfrak{m}[t^{-1}] + A[t]$ of the Laurent polynomial ring $A[t, t^{-1}]$ with the $\mathbb{Z}$-grading induced by the grading on $A[t, t^{-1}]$.
As an additive group $B$ decomposes into a direct sum of its homogeneous components $\oplus_{k\in\mathbb{Z}} B_k$,
 where each $B_k \subseteq B$ is equal either to $A\cdot t^k$ for $k \geq 0$ or to $\mathfrak{m} \cdot t^k$ for $k<0$.

@@

Denote by $i\colon G_\infty \to \St(\Phi, B)$ the map induced by the obvious embedding of $\mathcal{X}_\infty$ into the set of 
 Steinberg generators of $\St(\Phi, B)$.  
Using~\eqref{eq:H1ii} multiple times it is not hard to show that the map $j\colon \St(\Phi, B) \to G_\infty$ given by
 $j(x_\alpha(b)) = \prod x_\alpha(b_i)$, where $b = \sum b_i$ is the decomposition of $b$ into a finite sum of its homogeneous components $b_i\in B_i$, is a well-defined map.
It is clear that $i$ and $j$ are mutually inverse. 
\end{proof}

@@

>>>>

\section{Rehmann theorem for Laurent polynomials}
Let $A$ be arbitrary commutative unital ring and $\mathfrak{m}$ be its ideal.
Denote by $B$ the subring $\mathfrak{m}[t^{-1}] + A[t]$ of the Laurent polynomial ring $A[t, t^{-1}]$ with the $\mathbb{Z}$-grading induced by the grading on $A[t, t^{-1}]$.
As an additive group $B$ decomposes into a direct sum of its homogeneous components $\oplus_{k\in\mathbb{Z}} B_k$,
 where each $B_k \subseteq B$ is equal either to $A\cdot t^k$ for $k \geq 0$ or to $\mathfrak{m} \cdot t^k$ for $k<0$.

@@

Denote by $i\colon G_\infty \to \St(\Phi, B)$ the map induced by the obvious embedding of $\mathcal{X}_\infty$ into the set of 
 Steinberg generators of $\St(\Phi, B)$.  
Using~\eqref{eq:H1ii} multiple times it is not hard to show that the map $j\colon \St(\Phi, B) \to G_\infty$ given by
 $j(x_\alpha(b)) = \prod x_\alpha(b_i)$, where $b = \sum b_k$ is the decomposition of $b$ into a finite sum of its homogeneous components $b_k\in B_k$, is a well-defined map.
It is clear that $i$ and $j$ are mutually inverse. 
\end{proof}

@@

\begin{lemma} \label{lem:3.1f} Let $A$ be a local ring then any element $\alpha \in \St(\Phi, A)$ can be presented as a product 
$ $

\end{lemma}
